\input{title.tex}

### 2022-05-29 docs/papers/01_manuscript/04_discussion.tex
fix(discussion-model): fix a sentence according to Wen's comment (email)

% \subsection{Linking structures with ISs outcomes}
\label{discussion-2}
% discussion-2: 机制解释
Different individual provinces' water-use responses to the institutional shifts also support influences from SES structures.
Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS.
This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
Therefore, we theoretically abstracted the structures associated with the structural changes induced and analyzed how different water allocation structures shape different outcomes.
Assuming that water is the factor input with decreasing marginal output of each province, we discuss the marginal return and optimal water use under three different cases (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
The incentive for water overuse (compared to the water quotas) in each province derives from the mismatch between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive of water use, leading to higher water use.
Therefore, the water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under the unified allocation.
Our model interprets the results from structural perspectives: excessive water use incentive induces the acceleration of extracting resources for future economic growth, and a unified institution is indispensable for sustainable water use.

>>>>

% \subsection{Linking structures with ISs outcomes}
\label{discussion-2}
% discussion-2: 机制解释
Different individual provinces' water-use responses to the institutional shifts also support influences from SES structures.
Our results show that the correlation between current water use and changed (increased or decreased) water use was significant after the 87-WAS.
This ``major users use more'' pattern supports the hypothesis that separated stakeholder (individual province here) decides on linked ecological units for output maximization (water use).
Therefore, we theoretically abstracted the SES structures and analyzed how different structures shape different outcomes with provincial heterogeneity.
Assuming that water is the factor input with decreasing marginal output of each province, we discuss the marginal return and optimal water use under three different cases (analogy to Figure~\ref{structure}~C, see \nameref{sec:model}~Figure~\ref{fig:model}, detailed derivation in \textit{Appendix~\nameref{secS4}}).
The incentive for water overuse (compared to the water quotas) in each province derives from the mismatch between the benefits and costs of water use.
Until water-use decisions are consolidated into unified management, each stakeholder’s expectation that current water use helps bargain for a favorable water quota may intensify the incentive of water use, leading to higher water use.
Therefore, the water users with higher capability are more stimulated by institutional shifts and away from the theoretically optimal water use under the unified allocation.
Our model interprets the results from structural perspectives: excessive water use incentive induces the acceleration of extracting resources for future economic growth, and a unified institution is indispensable for sustainable water use.
